---
title: "Imputation_results_1"
author: "Huma Shehwana"
date: "2024-03-06"
output: html_document
---

# Data 
## Model 
sigma <- matrix(data = c(1, 0.7, 0.7, 1), 
                                ncol = 2)

simdata <- replicate(n = Num_ds, 
                      expr = mvtnorm::rmvnorm(n = 1000, 
                                             mean = c(8, 3), 
                                             sigma = sigma) %>% 
                      as_tibble() %>% # make into a tibble
                      rename(x = V1, z = V2) %>% # rename columns
                      mutate(y = 6 * x + 3 * z + rnorm(1000)), # add y
                      simplify = FALSE) # keep as list of generated sets
                      
                      
                      
Number of datasets = 10

missing value proportion = 20%, 30%, 40%, 50%, 60%, 70%, 80%, 90%


## Mice default setting
```{r setup}
library(DT)
load("MI_default.RData")
eval_default
```


## Mice CART algorithm

```{r }
load("MI_CART.RData")
eval_CART


```


## Mice RF algorithm

```{r }
load("MI_RF.RData")
eval_RF

```


## XGBoost default parameter with subsampling

```{r }
load("MI_xgb.RData")
eval_xgb
```

```{r , echo = FALSE, message=FALSE, fig.align='center', out.width="100%", out.height=500}
knitr::include_graphics("/Users/Shehw001/Documents/GitHub/mice/Training_test_XGBDefault_subsample70.pdf")
```

## XGBoost default parameter without subsampling

```{r }
load("MI_xgb_nosub.RData")
eval_xgb_nosub
```

```{r , echo = FALSE, message=FALSE, fig.align='center', out.width="100%", out.height=500}
knitr::include_graphics("/Users/Shehw001/Documents/GitHub/mice/Training_test_XGBDefault_nosub.pdf")
```


## XGBoost bayesian optimization of hyperparameters  - using a random vairable

```{r }
load("MI_xgb_param_random_maxit5.RData")
eval_xgb_param_random_maxit5
```

```{r , echo = FALSE, message=FALSE, fig.align='center', out.width="100%", out.height=500}
knitr::include_graphics("/Users/Shehw001/Documents/GitHub/mice/Training_test_XGB_param_random_maxit5.pdf")
```



## XGBoost bayesian optimization of hyperparameters  - using all variable

```{r }
load("MI_xgb_param_all_maxit5.RData")
eval_xgb_param_all_maxit5b
```

```{r , echo = FALSE, message=FALSE, fig.align='center', out.width="100%", out.height=500}
knitr::include_graphics("/Users/Shehw001/Documents/GitHub/mice/Training_test_XGB_param_all_maxit5.pdf")
```

